The five pillars of computational reproducibility: Bioinformatics and beyond

### 2023-05-30 manuscript/5pillars.Rmd
acknowledgements

Similarly, the [Streamlit](https://streamlit.io/) tool, which was originally invented for creating
Python-based web dashboards but is equally capable of generating data science reports
[e.g.: @Nantasenamat2023-wr].

@@

The key technological advances enabling the five pillars approach have been around for about a decade,
yet progress on integrating these into computational research publications has been minimal.
Part of the problem is the incentive structures in academia, with funding bodies and journals are
focused on novel research directions rather than confirming previous findings
[@Kaelin2017-id; @Munafo2017-ty; @Diong2021-is].
Indeed the number of systematic replication studies in bioinformatics remains small
(e.g.: [@Ioannidis2009-hv; @Zaringhalam2020-ms; @Samuel2022-ha]), so we don't have much of a grasp as to how severe the
problem actually is.

@@

I am grateful to the individuals who provided feedback on an earlier draft of the concept including
Dr Aziz Khan (Stanford University),
Dr Sriganesh Srihari (QIMR Berghofer Medical Research Institute),
Dr Barbara Zdrazil (EMBL-EBI) and Dr Irene López Santiago (EMBL-EBI).

>>>>

@@

The key technological advances enabling the five pillars approach have been around for about a decade,
yet progress on integrating these into computational research publications has been minimal.
Part of the problem is the incentive structures in academia, with funding bodies and journals are
focused on novel research directions rather than confirming previous findings
[@Kaelin2017-id; @Munafo2017-ty; @Diong2021-is].
Indeed the number of systematic replication studies in bioinformatics remains small
[@Zaringhalam2020-ms ; @Ioannidis2009-hv; @Samuel2022-ha] so we don't have much of a grasp as to how severe the
problem actually is.

@@

We are grateful to the individuals who provided feedback on an earlier draft of the concept including
Dr Aziz Khan (Stanford University),
Dr Sriganesh Srihari (QIMR Berghofer Medical Research Institute),
Dr Barbara Zdrazil (EMBL-EBI) and
Dr Irene López Santiago (EMBL-EBI).

This research was supported by use of the Nectar Research Cloud, a collaborative Australian research
platform supported by the NCRIS-funded Australian Research Data Commons (ARDC).

## Availability of materials

Code repository: https://github.com/markziemann/5pillars
